---
title: "Instructions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


If you want to run the code in the file `music_artists_project.Rmd` on your local machine, you can follow two approaches:

### 1. Without data extraction

You can run the code without extracting data from the APIs or scraping the Rolling Stone's article again. Simply pull the entire GitHub repository including the `data` folder. If you have saved the entire repo on your local machine, you can execute the code chunks that are not labeled with `eval=False`. This will prevent scraping or extracting the data again.

### 2. With data extraction

If you want to extract the data from our data sources again, you can do so by executing each code chunk, including the ones labeled with `eval=False`. However, you might have to modify the code slightly depending on your folder structure. Firstly, you need to set up your own secret keys on the [Spotify API](https://developer.spotify.com/documentation/web-api/tutorials/getting-started) and the [LastFM API](https://www.last.fm/api). For the Spotify API, you must save the client ID and client Secret as `CLIENT_ID=...` and `CLIENT_SECRET=...` in a document called `spotify_api.env`. For the LastFM API, you must save the key and the shared secret as `KEY=...` and `SHARED_SECRET=...` in a document called `lastfm_api.env`. Create a folder called `R_Environs`, which you save in the `Documents` folder on you local machine. Then, save the .env files in the `R_Environs` folder.

If you want to save the .env files differently, you need to modify the paths when calling `readRenviron` in the code:

```{r code changes for running the markdown locally, echo=TRUE, eval=FALSE}

# Replace "../../Documents/R_Environs/spotify_api.env" with your own path
readRenviron("../../Documents/R_Environs/spotify_api.env") 

# Replace "../../Documents/R_Environs/lastfm_api.env" with your own path
readRenviron("../../Documents/R_Environs/lastfm_api.env")
```
